---
title: "Read Excel data sheet"
author: "Anja Eggert"
date: "`r Sys.Date()`" 
editor: visual
code-fold: false
toc: true
format: html
self-contained: true
theme: readable
#bibliography: references.bib
---

# Reproducibility workshop

This code reads in an example *Excel* data table.

# Libraries

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r, libraries, warning=FALSE, message=FALSE, echo=TRUE}
library(kableExtra)  # html-table
library(readxl)      # read Excel files
library(tidyverse)   # tidy universe
```

# Read data

By default, the working directory for rendering files within a project is the directory of the file itself, here the subdirectory `code`.

You can play setting different arguments, e.g. exclude `.name_repair = "universal"`

```{r}
dat <- read_xlsx("../data/mydata.xlsx",
                 na = "a", .name_repair = "universal")
```

The `echo: false` option disables the printing of code (only output is displayed).

## Data adjustments

-   define variables as factors
-   define dates as date

```{r}
dat <- dat %>% 
  # make factors
  mutate_at(vars(SCHLNR,
                 RASSE,
                 HERK,
                 Haltung) , ~as.factor(.)) %>% 
  # make date
  mutate_at(vars(GEBDAT,
                 SCHLDAT) , ~as.Date(.))
```

## Create data table

```{r}
dat %>% 
  kable(caption = "Data set") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                font_size = 12) %>% 
  scroll_box(width = "800px", height = "500px")
```

# Plot data

```{r}
plot <- dat %>%
  ggplot(aes(x = Haltung,
             y = Sum.PUFAmg,
             fill = RASSE)) +
  geom_boxplot(col = "grey30",
               outlier.shape = NA, width=0.75,
               position = position_dodge(0.75)) +
  geom_point(aes(shape = HERK),
             col = "grey60", size = 2.5,
             position = position_jitterdodge()) +
  scale_y_continuous(limits = c(0, 400),
                     expand = c(0, 0),
                     breaks = seq(0,400,50)) +
  scale_fill_manual(values = c("#440154FF", "#21908CFF", "#FDE725FF")) +
  labs(x = "Haltung",
       y = "Summe PUFAs (mg)") +
  theme_bw() +
  guides(fill = guide_legend(override.aes = list(shape = NA)))
```

```{r, fig.height=10, fig.width=10, warning=FALSE}
plot
```

## Save plot

```{r}
png("../plots/myplot.png",
    width = 200, height = 180, units = "mm",
    pointsize = 10, res = 600)

plot

dev.off()
```

# How to cite R

"All analyses were performed using R Statistical Software (version 4.2.0; R Core Team 2022)".

Reference: R Core Team (2022). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. URL https://www.R-project.org/.

```{r, cite-r}
citation()
version$version.string
```

```{r, cite-packages}
citation("kableExtra")
citation("tidyverse")
```

# Session Info

```{r, session}
sessionInfo()
```
